---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

  [![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)   [![Travis build status](https://travis-ci.org/ColinFay/dockerfiler.svg?branch=master)](https://travis-ci.org/ColinFay/dockerfiler)
  
# dockerfiler

Easy Dockerfile Creation from R.

## Installation

You can install dockerfiler from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("colinfay/dockerfiler")
```

## Basic worflow 

By default, Dockerfiles are created with `FROM "rocker/r-base"`.
You can set another FROM in `new()`

```{r}
library(dockerfiler)
# Create a dockerfile template
my_dock <- Dockerfile$new()
my_dock$MAINTAINER("Colin FAY", "contact@colinfay.me")
```

Wrap your raw R Code inside the `r()` function to turn it into a bash command with `R -e`.

```{r}
my_dock$RUN(r(install.packages("attempt", repo = "http://cran.irsn.fr/")))
```

Classical Docker stuffs:

```{r}
my_dock$RUN("mkdir /usr/scripts")
my_dock$RUN("cd /usr/scripts")
my_dock$COPY("plumberfile.R", "/usr/scripts/plumber.R")
my_dock$COPY("torun.R", "/usr/scripts/torun.R")
my_dock$EXPOSE(8000)
my_dock$CMD("Rscript /usr/scripts/torun.R ")
```

See your Dockerfile : 

```{r}
my_dock
```

If you've made a mistake in your script, you can switch lines with the `switch_cmd` method. This function takes as arguments the positions of the two cmd you want to switch : 

```{r}
# Switch line 8 and 7
my_dock$switch_cmd(8, 7)
my_dock
```

You can also remove a cmd with `remove_cmd` : 

```{r}
my_dock$remove_cmd(8)
my_dock
```

This also works with a vector
```{r}
my_dock$remove_cmd(5:7)
my_dock
```

Save your Dockerfile 

```{r eval = FALSE}
my_dock$write()
```

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By participating in this project you agree to abide by its terms.
