---
title: "Getting started with dockerfiler"
author: "Colin Fay"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{getting_started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# dockerfiler

Easy Dockerfile Creation from R.

## Installation

You can install dockerfiler from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("remotes")
remotes::install_github("colinfay/dockerfiler")
```

Or from CRAN with : 

```{r, eval = FALSE}
install.packages("dockerfiler")
```

## Basic worflow 

By default, Dockerfiles are created with `FROM "rocker/r-base"`.

You can set another FROM in `new()`

```{r}
library(dockerfiler)
# Create a dockerfile template
my_dock <- Dockerfile$new()
my_dock$MAINTAINER("Colin FAY", "contact@colinfay.me")
```

Wrap your raw R Code inside the `r()` function to turn it into a bash command with `R -e`.

```{r}
my_dock$RUN(r(install.packages("attempt", repo = "http://cran.irsn.fr/")))
```

Classical Docker stuffs:

```{r}
my_dock$RUN("mkdir /usr/scripts")
my_dock$RUN("cd /usr/scripts")
my_dock$COPY("plumberfile.R", "/usr/scripts/plumber.R")
my_dock$COPY("torun.R", "/usr/scripts/torun.R")
my_dock$EXPOSE(8000)
my_dock$CMD("Rscript /usr/scripts/torun.R ")
```

See your Dockerfile : 

```{r}
my_dock
```

If you've made a mistake in your script, you can switch lines with the `switch_cmd` method. This function takes as arguments the positions of the two cmd you want to switch : 

```{r}
# Switch line 8 and 7
my_dock$switch_cmd(8, 7)
my_dock
```

You can also remove a cmd with `remove_cmd`: 

```{r}
my_dock$remove_cmd(8)
my_dock
```

This also works with a vector:

```{r}
my_dock$remove_cmd(5:7)
my_dock
```

`add_after` add a command after a given line. 

```{r}
my_dock$add_after(
  cmd = "RUN R -e 'remotes::install_cran(\"rlang\")'", 
  after = 3
)
```


Save your Dockerfile:

```{r eval = FALSE}
my_dock$write()
```

## Create a Dockerfile from a DESCRIPTION 

You can use a DESCRIPTION file to create a Dockerfile that installs the dependencies and the package.

```{r, eval = FALSE}
my_dock <- dock_from_desc("DESCRIPTION")

my_dock$CMD(r(library(dockerfiler)))

my_dock$add_after(
  cmd = "RUN R -e 'remotes::install_cran(\"rlang\")'", 
  after = 3
)
```

